|

### 2022-12-22 appendix/appendix.Rmd
production version

---
title: |
       | Supplementary Material for "Vigilantism and Institutions: Understanding Attitudes toward Lynching in Brazil"
author:
  - Danilo Freire[^danilo]
  - David Skarbek[^david]
date: \today
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: ../article/references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    highlight: haddock
    toc: true
    toc_depth: 3
    keep_tex: no
    template: template.latex
---

>>>>

---
title: |
       | Supplementary Material for "Vigilantism and Institutions: Understanding Attitudes toward Lynching in Brazil"
author:
  - Danilo Freire[^danilo]
  - David Skarbek[^david]
date: December 16, 2022
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: ../article/references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    highlight: haddock
    toc: true
    toc_depth: 3
    keep_tex: no
    template: template.latex
---
